FAIR theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2025-02-04 manuscript.Rmd
add abstract

abstract: |
  Test test.
keywords          : "fairtheory, meta theory, theory formation, cumulative science, formal models"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')))`"
bibliography      : "theory-specification.bib"
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            :
  papaja::apa6_pdf: default
  md_document: default
---

>>>>

abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.md'))))`"
keywords          : "fairtheory, meta theory, theory formation, cumulative science, formal models"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')))`"
bibliography      : "theory-specification.bib"
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            :
  papaja::apa6_pdf: default
  md_document: default
---
